---
title: "Homework 1"
author: "Your Name Here"
subtitle: "Spring 2024"
header-includes:
    - \usepackage{amsmath, amssymb}
    - \usepackage{setspace} 
output: pdf_document
---

\onehalfspacing

```{r setup, include=FALSE}
#Use this code chunk to include libraries, and set global options.
knitr::opts_chunk$set(echo = TRUE)
options(pillar.sigfig=6)
library(tidyverse)
```

### Instructions

- This homework is due in Gradescope on Wednesday April 10 by midnight PST. There is a 15 minute grace period and submissions made during this time will not be marked as late. Any work submitted past this period is considered late.  

- Please answer the following questions in the order in which they are posed. 

- Don't forget to (i) make a local copy this document for your work and to (ii) knit the document frequently to make sure there are no compilation errors. 

- When you are done, download the PDF file as instructed in section and submit it in Gradescope. 
* * *

### Exercises

1. (Two Researchers) In a sample of 1000 independent observations - $X_1,X_2,\dots,X_{1000}$ -  generated from a distribution with mean $\mu_0$ and known standard deviation 1, a
researcher (call them researcher 1) testing $H_0:\mu_0=0$ against $H_1:\mu_0 > 0$ rejects the null hypothesis at level 0.01 (highly significant).  

a. Find the rejection region for test conducted by researcher 1.  In other words, what is the minimum value of $\bar{x}_{obs}$ for which they will reject $H_0$? (Show your work; do any calculations in R showing your code)

b. Another researcher (call them researcher 2) using a sample of 100 independent observations - $Y_1,Y_2,\dots, Y_{100}$ - generated from a distribution with mean $\nu_0$ and known standard deviation 1  tests $H_0:\nu_0=0$ against $H_1: \nu_0 > 0$ and rejects the null hypothesis at level 0.05 (significant). Find the rejection region for test conducted by researcher 2.  In other words, what is the minimum value of $\bar{y}_{obs}$ for which they will reject $H_0$? (Show your work)


c. Which of $\mu_0$ or $\nu_0$ do you think is (likely) larger? Why? (There is no way to definitively know, I am interested in your ability to reason and explain ideas in your own words)


2. (Rate of passage) The	number	of electrons	produced	by	the	passage	of	an	alpha	particle through a	container	of a	given	medium	is	known	to	have	a	Poisson	 distribution with (unknown) rate $\lambda_0$.	Let $X_1, X_2, \dots,X_{100}$ denote the electron production of one hundred randomly selected particles passing	through	the	container at various times. 
Suppose we observe $\bar{x} = 9.4$. Calculate a 95% large sample confidence interval for the rate $\lambda_0$. Show your steps.

    Hint: the rate $\lambda_0$ is just a population mean. What does the CLT say about the sampling distribution of $\bar{X}$?


3. (Mean of means) Using a random sample of 25 observations - $X_1,X_2,\dots,X_{25}$ -  from a  population with (unknown) mean $\mu_1$ and (known) standard deviation $\sigma_1$, a 95\% large sample confidence interval for $\mu_1$ was $[1.37, 1.53]$. 

   Similarly using an independent sample of 36 observations - $Y_1, Y_2, \dots, Y_{36}$ - from a population with (unknown) mean $\mu_2$ and (known) standard deviation $\sigma_2$, a 95\% large sample confidence interval for $\mu_2$ was $[1.17, 1.29]$.

   Derive a large sample  95% confidence interval for  
   $$\mu = \frac{\mu_1 + \mu_2}{2}$$
   and calculate it for this example.
   
   Hint: see problem 1 on HW 6 from STAT 341. What is your estimator of $\mu$? Consider its sampling distribution according to the CLT.


4. (Elvin makes noise) Elvin has developed a method for constructing a confidence interval for a parameter $\theta_0$ in a certain model, and is doing simulations to see how well it covers the true value of the parameter across many samples. He generates $B = 1,000$ samples, each of size $n$, from the model with $\theta_0=\frac{1}{2}$, and for each sample he calculates the interval using a confidence level of 95%, and then notes whether the confidence interval contains $\frac{1}{2}$ in it. You can see his results in the file `elvin_results.csv`.

a. Write code to calculate his simulated coverage rate. Then print your answer. (You will need to read in the CSV file)

```{r problem 4a, message= F, warning = F}
#read in data and then print out simulated coverage rate

```

b. Since his simulated coverage rate isn't exactly 95%, Elvin is wondering if his simulation results indicate that the confidence level of his intervals differs from 0.95.  
Suppose $X_i$ denotes whether the $ith$ confidence interval covers the true value $\frac{1}{2}$. Then $X_1,X_2,\dots, X_{1000} \overset{i.i.d.}{\sim} Bernoulli(\pi_0)$ where $\pi_0$ is the probability that a randomly generated confidence interval using Elvin's method will \emph{actually} cover the true value. Help Elvin calculate the P-value for testing $H_0: \pi_0 = 0.95$. What should he conclude about whether the difference in his results from 0.95 is due to simulation noise? 
   
c. How high or low must the simulated coverage rate be for Elvin to suspect that the true coverage rate of his intervals is not 95%? Explain. (Assume we are using the threshold of significance $\alpha = 0.05$. )
   
d. If Elvin had thought ahead, he could have done a calculation to ensure that his simulated coverage rate would be within a certain margin of error of the true  $\pi_0$. How large would $B$ have to be in order for him to be 98% confident that the simulated coverage would be within 0.005 of the true $\pi_0$.   (You may use $\pi_0 = \frac{1}{2}$ for the standard error in this calculation)