---
title: "Problem Section 7"
subtitle:  "Likelihood Inference"
graphics: yes
output: pdf_document
header-includes:
    - \usepackage{amsmath, amssymb}
    - \usepackage{framed}\definecolor{shadecolor}{rgb}{0.949,0.949,0.949}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(maxLik)
```

\begin{shaded}

\textbf{Learning Outcomes}

The problems are designed to build conceptual understanding and problem-solving skills. The emphasis is on learning to find, evaluate and build confidence. The specific tasks include: 

  
   - Perform inference using the large sample distribution of the MLE
   
   - Calculate the likelihood ratio test statistic for significance testing 
   
   - Back up and support work with relevant explanations


\end{shaded}

* * *

## Exercises 

1. Suppose the number of students who arrive late to each of 10 consecutive lectures can be modeled as independent draws from a Poisson distribution with rate $\lambda$:
$$f_{\lambda}(x) = \frac{ e^{-\lambda}\:\lambda^{x}}{x!} \ \ \ x = 0,1,2,\dots$$
The data are observed as follows $x_1=0, x_2=0,x_3=0,x_4=1,x_5=1,x_6=1,x_7=2,x_8=2,x_9=3,x_{10}=3$. \footnote{note: $x_i$ denotes the number of students who were late to class $i$}

a. Calculate the MLE $\widehat{\lambda}_0^{mle}$ where $\lambda_0$ is the true value of the parameter which generated our data.   (see Example 24.5, slide 28 of slidedeck labeled 24.1-24.2)

b. The MLE should be familiar to you. Estimate its standard error.


c. Find the observed information $$-\ell^{\prime \prime}(\widehat{\lambda}_0^{mle}) = - \left. \frac{d^2}{d\lambda^2} \ln\left[L(\lambda) \right] \right\rvert_{\widehat{\lambda}_0^{mle}}.$$ How is related to your answer from part b?

d. Use the large sample normality of the MLE to calculate an approximate 95% confidence interval estimate for $\lambda_0$.

e. Write code to examine the quality of the second-order approximation to the log-likelihood upon which your confidence interval from part d is based. 

f. Suppose we wish to test $H_0: \lambda_0 = \lambda_0^{null}$ versus $H_1: \lambda_0 \neq \lambda_0^{null}$. Calculate the likelihood ratio test statistic:
$$W = 2 \ln\left[ \frac{L(\widehat{\lambda}_0^{mle})}{L(\widehat{\lambda}_0^{null})} \right]$$ for testing $H_0: \lambda_0^{null}=1$.

g. Calculate the (large sample) P-value associated with your test statistic from part e. That is assume $W \sim \chi^2_1$ under the null hypothesis. 

h. Since $n=10$ is not really a large sample, an alternative approach is to calculate an empirical P-value.  Take a look at Example 20.4 on page 39 from slidedeck labeled 20.1 - 20.2 in STAT 341 where I show you how to calculate one for a Poisson model. Write code below to find the empirical P-value for the likelihood ratio test statistic $W$ from part e.


    ```{r}
    set.seed(175)

    ```

